### 2021-04-27 assertions/doc/thesis-bernhardt/chapters/1-introduction.tex
Abstract

\chapter{Introduction}\label{chap:introduction}
Headed by Bitcoin in 2009 \cite{bitcoin-whitepaper}, the first generation of blockchain technology emerged in form of cryptocurrencies. However, their transactions are mostly limited to simple monetary transactions or registration of assets or ownerships \cite{alharby_blockchain_2017}. More recent blockchains, considered as the second generation, aim to provide a platform for building more sophisticated and complex applications on top of the technology. Some prominent examples for such blockchains are Ethereum \cite{eth-whitepaper}, Tezos \cite{goodman_tezos_2014} or Cardano \cite{cardano_essay}, which plans to introduce smart contracts in an update this year \cite{cardano_alonzo}. Blockchain-based applications are built with smart contracts, programs written in Turing-complete languages. Running a smart contract generates costs proportional to the amount and complexity of computations, as well as its storage usage \cite{alharby_blockchain_2017}. These fees, often measured in a unit called ``gas'', have to be paid for by the user in order to compensate the miners for their efforts \cite{narayanan_bitcoin}. This creates a powerful incentive to keep smart contracts simple and efficient. In reality, however, meaningful applications still might need to perform resource intensive computations or store larger amounts of data. Not only can such applications generate unsustainable costs when executed on the blockchain, but they may also reach gas limits imposed by the blockchain's protocol. \\
In order to avoid these costs and restrictions, such an application could perform some computations outside of the blockchain context (i.e., off-chain) and only submit the results to a smart contract as an input parameter for further processing or recording. By trusting that the submitted results are correct, this approach raises both safety and security issues. Invalid results can be submitted unintentionally as a result of a wrong computation, or a third party may pass them intentionally to cause harm or capitalize on it. Consequently, submitted parameters should be validated before the smart contract is executed. Although in many cases, verifying a solution takes less time than computing the result itself (cf. NP-hard problems \cite{nph_problems} or sorting algorithms \cite{review_sorting}\cite{cpp_issorted}), the generated costs for checking the validity increase with the size of the input. \\
Consider the smart contract \texttt{Example}, which is shown in \lstref{lst:prime} and features a function \texttt{f}. The function takes an input value \texttt{p} of type integer and should make use of the assumption that \texttt{p} is a prime number.
\begin{lstlisting}[caption=Smart contract with a function expecting a prime number \cite{thiemann_2020}, numbers=none, language=Solidity, label=lst:prime]
contract Example {
	function f ( int p ) public {
	// assume p is prime
	...
	}
}
\end{lstlisting}
The assumption ``$p$ is a prime number'' can be expressed with the following explicit assertion in predicate logic: 
\begin{equation}\label{eq:prime}
    (\forall n) (2 \le n \le \sqrt{p}) \Rightarrow (p \% n) \neq 0
\end{equation}
To check whether this property holds for $p$, the contract has to execute a loop over the range $[2, \sqrt{p}]$. Assuming that computing the body of the loop takes constant time, this test has a time complexity of $\mathcal{O}(\sqrt{p})$ and therefore generates costs linear in $\sqrt{p}$ on top of the cost for executing the actual contract. Thus, a mechanism is required that allows the smart contract to make use of the result computed by an off-chain source, without having to check its validity locally with scaling costs.

@@

\section{Objective}
This thesis proposes a model for the portrayed approach of a distributed assertion checking scheme, in order to make more efficient use of off-chain computations. In this model, results of such computations are validated on-chain by the validators of the network. In order to do so, they invoke assertion smart contracts, which point-wise check the validity of certain properties. When claiming an assertion failure, a validator publishes a counterexample to be scrutinized by the other validators. If they come to a consensus about the invalidity, the result is rejected. Provided that the assertion is cheaper than the computation itself, the purpose of this proposal is not only to reduce financial costs for the users, but also to overcome limitations in scalability imposed by gas limits.

>>>>

\chapter{Introduction}\label{chap:introduction}
Headed by Bitcoin in 2009 \cite{bitcoin-whitepaper}, the first generation of blockchain technology emerged in form of cryptocurrencies. However, their transactions are mostly limited to simple monetary transactions or registration of assets or ownerships \cite{alharby_blockchain_2017}. More recent blockchains, considered as the second generation, aim to provide a platform for building more sophisticated and complex applications on top of the technology. Some prominent examples for such blockchains are Ethereum \cite{eth-whitepaper}, Tezos \cite{goodman_tezos_2014} or Cardano \cite{cardano_essay}, which plans to introduce Smart Contracts in an update this year \cite{cardano_alonzo}. Blockchain-based applications are built with Smart Contracts, programs written in Turing-complete languages. Running a Smart Contract generates costs proportional to the amount and complexity of computations, as well as its storage usage \cite{alharby_blockchain_2017}. These fees, often measured in a unit called ``gas'', have to be paid for by the user in order to compensate the miners for their efforts \cite{narayanan_bitcoin}. This creates a powerful incentive to keep Smart Contracts simple and efficient. In reality, however, meaningful applications still might need to perform resource intensive computations or store larger amounts of data. Not only can such applications generate unsustainable costs when executed on the blockchain, but they may also reach gas limits imposed by the blockchain's protocol. \\
In order to avoid these costs and restrictions, such an application could perform some computations outside of the blockchain context (i.e., off-chain) and only submit the results to a Smart Contract as an input parameter for further processing or recording. By trusting that the submitted results are correct, this approach raises both safety and security issues. Invalid results can be submitted unintentionally as a result of a wrong computation, or a third party may pass them intentionally to cause harm or capitalize on it. Consequently, submitted parameters should be validated before the Smart Contract is executed. Although in many cases, verifying a solution takes less time than computing the result itself (cf. NP-hard problems \cite{nph_problems} or sorting algorithms \cite{review_sorting}\cite{cpp_issorted}), the generated costs for checking the validity increase with the size of the input. \\
Consider the Smart Contract \texttt{Example}, which is shown in \lstref{lst:prime} and features a function \texttt{f}. The function takes an input value \texttt{p} of type integer and should make use of the assumption that \texttt{p} is a prime number.
\begin{lstlisting}[caption=Smart contract with a function expecting a prime number \cite{thiemann_2020}, numbers=none, language=Solidity, label=lst:prime]
contract Example {
	function f ( int p ) public {
	// assume p is prime
	...
	}
}
\end{lstlisting}
The assumption ``$p$ is a prime number'' can be expressed with the following explicit assertion in predicate logic: 
\begin{equation}\label{eq:prime}
    (\forall n) (2 \le n \le \sqrt{p}) \Rightarrow (p \% n) \neq 0
\end{equation}
To check whether this property holds for $p$, the contract has to execute a loop over the range $[2, \sqrt{p}]$. Assuming that computing the body of the loop takes constant time, this test has a time complexity of $\mathcal{O}(\sqrt{p})$ and therefore generates costs linear in $\sqrt{p}$ on top of the cost for executing the actual contract. Thus, a mechanism is required that allows the Smart Contract to make use of the result computed by an off-chain source, without having to check its validity locally with scaling costs.

@@

\section{Objective}
This thesis proposes a model for the portrayed approach of a distributed assertion checking scheme, in order to make more efficient use of off-chain computations. In this model, results of such computations are validated on-chain by the validators of the network. In order to do so, they invoke assertion Smart Contracts, which point-wise check the validity of certain properties. When claiming an assertion failure, a validator publishes a counterexample to be scrutinized by the other validators. If they come to a consensus about the invalidity, the result is rejected. Provided that the assertion is cheaper than the computation itself, the purpose of this proposal is not only to reduce financial costs for the users, but also to overcome limitations in scalability imposed by gas limits.
